---
title: "Introduction to StatComp20051"
author: "Qihang Yang"
date: "2020/12/08"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to StatComp20051}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
## Overview

__StatComp20051__ is a R package developed to consider variable selection and estimation in high-dimensional regression with compositional covariates. __ftheta__ and __fSIGMA__ Generate the related parameters for multinormal distribution. __fZ__ and __fY__ generate compositional dataset and response vector. __fsto__ is a function of soft thresholding operator. __festimate__ find the estimation of coefficents for high dimensional compositional data.


### Codes for testing the preformance of festimate.R using simulation. 
  These functions are basic functions for simulation procedure, return compositional dataset, response vectory.
  
* Generate the mean vector for multinormal distribution.
```{r}
# p Dimension of the data.
# ter is length of nonzero components.
# co co*p is the mean of the nonzero components
ftheta <- function(p,ter,co)
{
  ttheta <- rep(0,p)
  for(ii in 1:ter)
  {
    ttheta[ii] <- log(co*p)
  }
  return(ttheta)  # return The mean vector for multinormal distribution.
}
```

* Generate correlation matrix for multinormal distribution.
```{r}
# rho:  cor(xi,xj) = rho^abs(i-j).
fSIGMA <- function(rho,p)
{
  repzero <- rep(0,p*p)
  SIGMA <- matrix(data = repzero, nrow = p, ncol = p)
  for(ii in 1:p)
  {
    for(jj in 1:p)
      SIGMA[ii,jj] <- rho^(abs(ii-jj))
  }
  return(SIGMA)  # return Correlation matrix.
}
```

* Generate compositional dataset, and apply log() on each component
```{r}
# p is dimension of the data. 
# m is the number of samples.
fZ <- function(m,p,ter,co,rho)
{
  SIGMAtemp <- fSIGMA(rho,p)
  thetatemp <- ftheta(p,ter,co)
  library(mvtnorm)
  wtemp <- rmvnorm(m, mean = thetatemp, sigma = SIGMAtemp)  #m rows and p columns
  rrepzero <- rep(0,m*p)
  xtemp <- matrix(data = rrepzero, nrow = m, ncol = p)
  for(ii in 1:m)
  {
    xexptemp <- exp(wtemp[ii,])
    sumexptemp <- sum(xexptemp)
    for(jj in 1:p)
      xtemp[ii,jj] <- xexptemp[jj]/sumexptemp
  }
  ztemp <- log(xtemp)
  return(ztemp)  # return Log of compositional dataset.
}
```

* Generate response vector.
```{r}
# zk is Log of componsional dataset.
# beta is Vector of coefficient. Sum(beta)=0.
# mean is mean vector when generating composional dataset.
# sd is standard error for error term in linear regression model.
fY <- function(zk,beta,mean,sd)
{
  q <- length(zk[,1])
  epsilontemp <- rnorm(q, mean , sd)
  y <- zk%*%beta+epsilontemp
  return(y)  # return Response vector.
}
```

* Function of soft thresholding operator.

$S_{\lambda }(t)=sgn(t)(|t|-\lambda )_{+}$ is the soft thresholding operator.

```{r}
# t is A number of input.
# lambda is Threshold.
fsto <- function(t,lambda)
{
  if(abs(t)<=lambda)
    return(0)
  else
  {
    if(t>0)
      return(t-lambda)
    else
      return(t+lambda)
  }  # return Number of fsto(t).  
}
```

### Find the estimation of coefficents for high dimensional compositional data, L1 and L2 penalized functions are used.

Here we propose an efficient, easily implemented algorithm based on an iterative modification of coordinate descent that involves combining it with the method of multipliers or the augmented Lagrangian method (Bertsekas, 1996) to deal with the constraint.

$$L_{\mu}(\beta,\gamma)=\frac{1}{2n}\left \| \gamma-Z\beta \right \|_{2}^{2}+\lambda \left \| \beta \right \|_{1}+\gamma\sum_{j=1}^{p}\beta_{j}+\frac{\mu}{2}\left ( \sum_{j=1}^{p}\beta_{j} \right )^{2}$$
```{r}
# expect a linear model, and the sum of the coefficietns equals 0.
# yy is a vector of response variable y
# ac1 is accuracy when getting an estimation of parameters. High accuracy means more accuracy results.
# ac2 is accuracy when getting an estimation of parameters. High accuracy means more accuracy results.
# lambda1 is coefficient for L1 penlized function
# lambda2 is coefficient for L2 penlized function
# Z is a matrix of independent variables. It should be log of the compositional data matrix, in which each row should sum to 1, and each component should be between 0 and 1.
festimate <- function(yy, Z, betastart, alphastart, ac1, ac2, lambda1, lambda2, mu)
{
  pp <- length(Z[1, ]) 
  nn <- length(Z[, 1])  
  beta1 <- rep(betastart, pp)  # betastart is starting vector for the estimation of coefficient beta.
  beta2 <- beta1+100
  alpha1 <- alphastart  # alphastart is starting vector for the estimation of lagrange multiplier for sum of the coefficients.
  alpha2 <- alphastart+100
  vv <- rep(0, pp)
  for(kk in 1:pp)
    vv[kk] <- sum(Z[, kk]*Z[, kk])/nn ##squared sum of each column
  
  while(sqrt(sum((beta1-beta2)*(beta1-beta2))+(alpha1-alpha2)^2)>ac2)
  {
    beta2 <- beta1+100   
    alpha2 <- alpha1
    while(sqrt(sum((beta1-beta2)*(beta1-beta2)))>ac1)
    {
      beta2 <- beta1
      for(jj in 1:pp)
      {
        tempj <- 0
        for(i in 1:nn)
        {
          tempj <- tempj+1/nn*(yy[i]-sum(Z[i,]*beta1)+Z[i,jj]*beta1[jj])*Z[i,jj]
        }
        tj <- tempj-mu*(sum(beta1)-beta1[jj]+alpha2)
        beta1[jj] <- 1/(vv[jj]+2*lambda2+mu)*fsto(tj,lambda1)  # mu is multiplier of the square of the sum of the coefficients in Lagrange method.
      }    
    }
    alpha2 <- alpha1
    alpha1 <- alpha2+sum(beta1)      
  }
  
  vec <- c(beta1, betastart, alphastart, ac1, ac2, lambda1, lambda2, mu)
  write.csv(vec,"temptempest.csv")
  file.append("tempest.csv", "temptempest.csv") 
  return(beta1)  # return Estimation of coefficients
}
```